Generating the Blueprints of the Java Ecosystem

### 2015-03-30 msr2015-camera-ready.tex
paper ready for submission

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Generating the Blueprints of the Java Ecosystem}

\author{\IEEEauthorblockN{Vassilios Karakoidas\IEEEauthorrefmark{1},
Dimitris Mitropoulos\IEEEauthorrefmark{2},
Georgios Gousios\IEEEauthorrefmark{3},
Diomidis Spinellis\IEEEauthorrefmark{1} and
Panos Louridas\IEEEauthorrefmark{1}}

@@

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. In general, it follows the same methodology presented in reference \cite{MKLGS14}.

Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects that contain several versions. In our experiment, we only used Java projects. For every Java project all versions were filtered out and only the latest was kept. The process to identify them was the following; Every project consists of two {\sc jar} files, one that contains a compiled version of the project and one that contains the source code. The projects that did not had both binary and source {\sc jar}s, were excluded from the experiment. When the source {\sc jar} file was downloaded, it was scanned for Java source files. If the source files were present in the archive, then the project was flagged as a valid Java project.

@@

The dataset also includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}. These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns~\cite{KARA14} as we illustrate in the following section.

@@

As we mentioned earlier, to produce our dataset we adopted a narrow selection process. In particular, we identified and analyzed only projects that were written in Java and had both the source code and the binary {\sc jar} available in the repository. The latter reduced significantly the number of projects that were analyzed, because many of them provided only the binary {\sc jar}. Since only \textit{clmt} analyses the source code, this resulted in the reduction of the number of measurements that exposed object-oriented and package design issues.

@@

We presented a dataset created by applying three different static analysis tools on Java projects coming from the Maven Central repository. The results invlove a variety of software metrics from program size to object-oriented design.
%In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates made in the repository.
We have also shown how our data can be used to extract meaningful results concerning {\sc dsl} usage in Java Projects.

>>>>

\begin{document}

\title{Generating the Blueprints of the Java Ecosystem}

\author{\IEEEauthorblockN{Vassilios Karakoidas\IEEEauthorrefmark{1},
Dimitris Mitropoulos\IEEEauthorrefmark{2},
Panos Louridas\IEEEauthorrefmark{1},
Georgios Gousios\IEEEauthorrefmark{3} and
Diomidis Spinellis\IEEEauthorrefmark{1}}

@@

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. In general, it follows the same methodology as Mitropoulos et al. \cite{MKLGS14}.

Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects that contain several versions. In our experiment, we only used Java projects. For every Java project all versions were filtered out and only the latest was kept. The process to identify them was the following; Every project consists of two {\sc jar} files, one that contains a compiled version of the project and one that contains the source code. The projects that did not have both binary and source {\sc jar}s, were excluded from the experiment. When the source {\sc jar} file was downloaded, it was scanned for Java source files. If the source files were present in the archive, then the project was flagged as a valid Java project.

@@

The dataset also includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}. These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns~\cite{KARA14} as we illustrate in the following section. In addition, the dataset covers a significant portion of the Maven repository, it can be used for large scale empirical studies.

@@

As we mentioned earlier, to produce our dataset we adopted a narrow selection process. In particular, we identified and analyzed only projects that were written in Java and had both the source code and the binary {\sc jar} available in the repository. The former reduced significantly the number of projects that were analyzed, because many of them provided only the binary {\sc jar}. Since only \textit{clmt} analyses the source code, this resulted in the reduction of the number of measurements that exposed object-oriented and package design issues.

@@

We presented a dataset created by applying three different static analysis tools on Java projects coming from the Maven Central repository. The results involve a variety of software metrics from program size to object-oriented design. We have also shown how our data can be used to extract meaningful results concerning {\sc dsl} usage in Java Projects.
